untitled

### 2016-04-21 model.tex
updated notes

\begin{align}\label{vshear}
  r\frac{\p \Omega^2}{\p z} = \frac{\p\ln{\rho}}{\p r}\frac{\p}{\p
    z}\left[c_s^2(1-\epsilon)\right] - \frac{\p\ln{\rho}}{\p z}
  \frac{\p}{\p r} \left[c_s^2(1-\epsilon)\right]. 
\end{align}

@@

\begin{align}
  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0,\\
  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, 
\end{align}  
where 
\begin{align}
  s \equiv \ln \frac{P}{\rho} = \ln{(1-\epsilon)} 
\end{align}
may be interpreted as the mixture entropy. The first equality is
similar to the usual defintion for gas entropy (with unit adiabatic
index). The second follows from the imposed equation of state,
Eq. \ref{eos}, with a constant sound-speed.

@@

\subsection{Locally isothermal gas perfectly coupled to dust} 
$c_s(r,z)$ is non-uniform, but $\tstop=0$.

>>>>

\begin{align}\label{vshear}
  r\frac{\p \Omega^2}{\p z} &= \frac{\p\ln{\rho}}{\p r}\frac{\p}{\p
    z}\left[c_s^2(1-\epsilon)\right] - \frac{\p\ln{\rho}}{\p z}
  \frac{\p}{\p r} \left[c_s^2(1-\epsilon)\right]\\  
  & = \frac{1}{\rho}\left(\frac{\p P}{\p r}\frac{\p s}{\p z} -\frac{\p
    P}{\p z}\frac{\p s}{\p r} \right),\notag
\end{align}
where
\begin{align}
   s \equiv \ln \frac{P}{\rho}
\end{align}
may be interpreted as the mixture entropy.

@@

\begin{align}
  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0,\\
  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0. 
\end{align}  
Here we may take $s=\ln{1-\epsilon}$ from the definition of $s$ and
the equation of state (Eq. \ref{eos}) with constant sound-speed.

%\begin{align}
%  s \equiv \ln \frac{P}{\rho} = \ln{(1-\epsilon)} 
%\end{align}
% The first equality is
%similar to the usual defintion for gas entropy (with unit adiabatic
%index). The second follows from the imposed equation of state,
%Eq. \ref{eos}, with a constant sound-speed.

@@

\subsection{Locally isothermal gas perfectly coupled to dust} 
$c_s(r,z)$ is non-uniform, but $\tstop=0$. Integral relation for
linear, axisymmetric waves with frequency $\sigma$ (see Appendix \ref{var_prin})
\begin{align}
&  \sigma^2\int\rho\left(|\dd v_r|^2 + |\dd v_z|^2\right)dV \notag\\
&= \int\left[ \rho
  |\dd v_r|^2A + \rho  \dd v_z \dd v_r^* B + \rho \dd v_z^*\dd v_r C +
  \rho |\dd v_z|^2 D\phantom{\frac{1}{1}}\right. \notag\\
&\phantom{===}  \left. + \frac{1}{P}\left|\nabla\cdot\left(P\dd
  \bm{v}\right)\right|^2\right]dV - \int P
  \left(\nabla\cdot\dd\bm{v}^*\right)\left(\dd\bm{v}\cdot\nabla\ln{c_s^2}\right)dV.
\end{align}
The real coefficients $A,B,C,D$ can be read off
Eq. \ref{integral_ex}. If $c_s$ is constant, $\sigma$ is real, and 
the first integral leads to the usual Solberg-Hoiland criteria for
axisymmetric stability. However, when $c_s$ is non-uniform, $\sigma$
is generally complex, implying instability. This is the usual vertical
shear instability.
